Reproducible Workflow on a Public Cloud for Computational Fluid Dynamics

### 2019-09-10 tex/MesnardoBarba2019.tex
add note about portability

Our in-house CFD software, PetIBM, relies on MPI to run applications on distributed-memory architectures.
The Poisson system is solved on distributed GPU devices using the NVIDIA AmgX library.
Thus, we used Azure instances of the NC-series, which feature a network interface for remote direct memory access (RDMA) connectivity, allowing nodes in the same pool to communicate over InfiniBand network.
The Docker images were specifically built to be able to run MPI applications on RDMA-capable virtual machines (such as the NC24r instance with a CentOS-based 7.3 HPC image) with multiple-instance tasks on Azure Batch service.
As of this writing, only Intel MPI 5.x versions are supported with the Azure Linux RDMA drivers.

>>>>

Our in-house CFD software, PetIBM, relies on MPI to run applications on distributed-memory architectures.
The Poisson system is solved on distributed GPU devices using the NVIDIA AmgX library.
Thus, we used Azure instances of the NC-series, which feature a network interface for remote direct memory access (RDMA) connectivity, allowing nodes in the same pool to communicate over InfiniBand network.
The Docker images were specifically built to be able to run MPI applications on RDMA-capable virtual machines (such as the NC24r instance with a CentOS-based 7.3 HPC image) with multiple-instance tasks on Azure Batch service.
As of this writing, only Intel MPI 5.x versions are supported with the Azure Linux RDMA drivers.
Both the Docker image and the configurations files for deploying the cloud resources give an interested reader the opportunity to reproduce our computations in an identical environment.
Even if this opportunity is not accompanied by portability---e.g., one may depend on a different MPI library to use a different system---the human-readable Docker files and configuration files do offer transparency.
